\chapter{定理环境}

\section{定理设置}

关于定理环境, 模板里也没有做特殊的设置. 用户可以自行决定使用 \LaTeX{} 本身的定理环境还是 \verb|amsthm| 增强的定理环境.

为了适配中文习惯. 可以使用 \verb|amsthm| 宏包提供的 \verb|\newtheoremstyle| 命令来新定义一种定理样式. 该命令有 9 个参数. 这里给出 ``定理'' 和 ``定义'' 两种定理样式.
\begin{verbatim}
\newtheoremstyle{ustctheorem}
  {\topsep}{\topsep}{\itshape}{}{\sffamily}{}{1em}{}
\newtheoremstyle{ustcdefinition}
  {\topsep}{\topsep}{}{}{\sffamily}{}{1em}{}
\end{verbatim}

下面的代码给出了常用的一些定理环境的定义.
\begin{verbatim}
\theoremstyle{ustctheorem}
\newtheorem{theorem}{定理}[section]
\newtheorem{proposition}[theorem]{命题}
\newtheorem{lemma}[theorem]{引理}
\newtheorem{corollary}[theorem]{推论}
\theoremstyle{ustcdefinition}
\newtheorem{definition}[theorem]{定义}
\newtheorem{example}[theorem]{例}
\newtheorem{remark}[theorem]{注}
\end{verbatim}

\section{定理测试}

\begin{definition}[option]\label{def:test}
  这个定义用于测试. It is used for testing. 这个定义用于测试. It is used for testing. 这个定义用于测试. It is used for testing. 这个定义用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{definition}

\begin{lemma}\label{lem:test}
  这个引理用于测试. It is used for testing. 这个引理用于测试. It is used for testing. 这个引理用于测试. It is used for testing. 这个引理用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{lemma}

\begin{proposition}\label{prop:test}
  这个命题用于测试. It is used for testing. 这个命题用于测试. It is used for testing. 这个命题用于测试. It is used for testing. 这个命题用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{proposition}

\begin{theorem}[option]\label{thm:test}
  这个定理用于测试. It is used for testing. 这个定理用于测试. It is used for testing. 这个定理用于测试. It is used for testing. 这个定理用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{theorem}

\begin{proof}
  这个证明用于测试. It is used for testing. 这个证明用于测试. It is used for testing. 这个证明用于测试. It is used for testing. 这个证明用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{proof}

\begin{remark}\label{rem:test}
  这个注用于测试. It is used for testing. 这个注用于测试. It is used for testing. 这个注用于测试. It is used for testing. 这个注用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{remark}

\begin{example}\label{ex:test}
  这个例子用于测试. It is used for testing. 这个例子用于测试. It is used for testing. 这个例子用于测试. It is used for testing. 这个例子用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{example}

\begin{corollary}\label{cor:test}
  这个推论用于测试. It is used for testing. 这个推论用于测试. It is used for testing. 这个推论用于测试. It is used for testing. 这个推论用于测试. It is used for testing. $f(x)=\sin x + \cos x$.
\end{corollary}

\section{Theorem}

\begin{definition}
  If the integral of function $f$ is measurable and non-negative, we define
  its (extended) \textbf{Lebesgue integral} by
  \begin{equation}\label{eq:test}
    \int f = \sup_g \int g,
  \end{equation}
  where the supremum is taken over all measurable functions $g$ such that
  $0 \leq g \leq f$, and where $g$ is bounded and supported on a set of
  finite measure.
\end{definition}

\begin{example}
  Simple examples of functions on $\mathbb{R}^d$ that are integrable
  (or non-integrable) are given by
  \begin{equation}
    f_a(x) =
    \begin{cases}
      |x|^{-a}, & \text{if } |x| \leq 1,\\
      0, & \text{if } x > 1.
    \end{cases}
  \end{equation}
  \begin{equation}
    F_a(x) = \frac{1}{1 + |x|^a}, \qquad \text{all } x \in \mathbb{R}^d.
  \end{equation}
  Then $f_a$ is integrable exactly when $a < d$, while $F_a$ is integrable
  exactly when $a > d$.
\end{example}

\begin{lemma}[Fatou]
  Suppose $\{f_n\}$ is a sequence of measurable functions with $f_n \geq 0$.
  If $\lim_{n \to \infty} f_n(x) = f(x)$ for a.e. $x$, then
  \begin{equation}
    \int f \leq \liminf_{n \to \infty} \int f_n.
  \end{equation}
\end{lemma}

\begin{remark}
  We do not exclude the cases $\int f = \infty$,
  or $\liminf_{n \to \infty} f_n = \infty$.
\end{remark}

\begin{corollary}
  Suppose $f$ is a non-negative measurable function, and $\{f_n\}$ a sequence
  of non-negative measurable functions with
  $f_n(x) \leq f(x)$ and $f_n(x) \to f(x)$ for almost every $x$. Then
  \begin{equation}
    \lim_{n \to \infty} \int f_n = \int f.
  \end{equation}
\end{corollary}

\begin{proposition}
  Suppose $f$ is integrable on $\mathbb{R}^d$. Then for every $\epsilon > 0$:
  \begin{enumerate}
    \renewcommand{\theenumi}{\roman{enumi}}
    \item There exists a set of finite measure $B$ (a ball, for example) such that
    \begin{equation}
      \int_{B^c} |f| < \epsilon.
    \end{equation}
    \item There is a $\delta > 0$ such that
    \begin{equation}
      \int_E |f| < \epsilon \qquad \text{whenever } m(E) < \delta.
    \end{equation}
  \end{enumerate}
\end{proposition}

\begin{theorem}
  Suppose $\{f_n\}$ is a sequence of measurable functions such that
  $f_n(x) \to f(x)$ a.e. $x$, as $n$ tends to infinity.
  If $|f_n(x)| \leq g(x)$, where $g$ is integrable, then
  \begin{equation}
    \int |f_n - f| \to 0 \qquad \text{as } n \to \infty,
  \end{equation}
  and consequently
  \begin{equation}
    \int f_n \to \int f \qquad \text{as } n \to \infty.
  \end{equation}
\end{theorem}

\begin{proof}
  Trivial.
\end{proof}
